GSE158422: DNA methylation in Lung squamous cell carcinoma - gene methylation enrichment analysis

### 2023-10-01 figs/GSE158422_split.Rmd
aggagg approach

@@

## AL: Aggregate limma

@@

#ttenrich is same

@@

>>>>

There are three approaches.
First, limma can be done first, followed by aggregation by gene and then enrichment
test (called LA).
Secondly, probe values can be aggregated by gene, followed by limma, followed by
enrichment test (AL).
Third, probe values can be aggregated to gene level, and then aggregated to gene set
level followed by limma test (AA).

@@

## AL: Aggregate limma functions

@@

## AA Aggregate-aggregate-limma functions

```{r,aafunc}

gsagg <- function(x,genesets,cores=1) {
  meds <- mclapply(1:length(genesets), function(i) {
    gs = genesets[[i]]
    xx <- x[rownames(x) %in% gs,]
    med <- apply(xx,2,median)
  },mc.cores=cores)
  mymed <- do.call(rbind,meds)
  rownames(mymed) <- names(genesets)
  as.data.frame(mymed)
}

aalimma <- function(agag,design) {
  fit.reduced <- lmFit(agag,design)
  fit.reduced <- eBayes(fit.reduced)
  dmagg <- topTable(fit.reduced,coef=ncol(design), number = Inf)
  return(dmagg)
}

aal <- function(mval,myann,genesets,design,cores=1) {
  medf <- chragg(mval,myann,cores=CORES)
  agag <- gsagg(x=medf,genesets=gs_symbols,cores=CORES)
  aal <- aalimma(agag=agag,design=design)
  return(aal)
}

aalres <- aal(mval=mval,myann=myann,genesets=gs_symbols,design=design,cores=CORES)

@@

laout

alout
